Methodology for Assessing the State of the Practice for Domain X

### 2020-05-01 StateOfPractice/Methodology/Methodology.tex
updated usability measures
added questionnaire and task criteria sections

\subsection{Empirical Measures}
 \begin {enumerate}
 \item Qualitative/Quantitative
 \item Pairwise Comparison methodology needs to be described
 \item Measure time to complete a task and compare actual with expected time of completion
 \item From a list of given tasks, measure how many tasks were completed correctly
\end {enumerate}

\subsection{Tools}
\begin {enumerate} 
\item Downloaded OBS to record experiment sessions
\end {enumerate}
\subsection{To do}
\begin {enumerate}
 \item Detail plan
 \item Describe Pairwise methodology
 \item Define tasks
 \item prepare survey questions
 \end {enumerate}

\section{Analytic Hierarchy Process}

>>>>

\subsection{Empirical Measures}
 \begin {enumerate}
 \item Qualitative/Quantitative
 \item Pairwise Comparison methodology needs to be described
 \item Measure time to complete a task and compare actual with expected time of completion
 \item From a list of given tasks, measure how many tasks were completed correctly
 \item Learnability
 \item Efficiency
 \item Memorability
 \item Errors
 \item Satisfaction
 \item Heuristic evaluation: Experts go through the interface to identify elements that violate usability heuristics.Popular because of its low cost and low time commitment
\end {enumerate}

\subsection{Nielsen’s Heuristics}
\begin{enumerate}
	\item Consistency: Check if standards and conventions in product design are followed
 \begin{itemize}
 	\item Sequences of actions (skill acquisition).
 	\item Color (categorization).
 	\item Layout and position (spatial consistency).
 	\item Font, capitalization (levels of organization).
 	\item Terminology (delete, del, remove, rm) and language (words, phrases).
 	\item Standards (e.g.,	blue underlined text for unvisited hyper links).
 \end{itemize}
\item Visibility: Users should be informed about what is going on with the system through appropriate feedback and display of information e.g. 
 \begin{itemize}
 \item What is the current state of the system?
 \item What can be done at current state?
 \item Where can users go?
 \item What change is made after an action?
 \end{itemize}
\item Match between system and world. The image of the system perceived by users should match the model the users have about the system. 
\begin {itemize}
\item User model matches system image.
\item Actions provided by the system should match actions performed by users.
\item Objects on the system should match objects of the task.
\end {itemize}
\item Minimalist: Any extraneous information is a distraction and a slow-down. 
\begin{itemize}
\item Less is more.
\item Simple is not equivalent to abstract and general.
\item Simple is efficient.
\item  Progressive levels of detail.
\end{itemize}
\item Minimize memory load. Users should not be required to memorize a lot of information to carry out tasks. Memory load reduces users’ capacity to carry out the main tasks. 
\begin{itemize}
\item Recognition vs. recall (e.g., menu vs. commands).
\item Externalize information through visualization.
\item Perceptual procedures.
\item Hierarchical structure.
\item Default values.
\item Concrete examples (DD/MM/YY, e.g., 10/20/99).
\item Generic rules and actions (e.g., drag objects).
\item Intuitive procedure
\end{itemize}
\item Informative feedback. Users should be given prompt and informative feedback about their actions. 
\begin{itemize}
\item Information that can be directly perceived, interpreted, and evaluated.
\item Levels of feedback (novice and expert).
\item Concrete and specific, not abstract and general.
\item Response time:\\
-0.1 s for instantaneously reacting;\\
-1.0 s for uninterrupted flow of thought;\\
-10 s for the limit of attention.
\end{itemize}
\item Flexibility and efficiency. Users always learn and users are always different. Give users the flexibility of creating customization and shortcuts to accelerate their performance. 
\begin{itemize}
	\item Shortcuts for experienced users.
	\item Shortcuts or macros for frequently used operations.
	\item Skill acquisition through chunking.
	\item Examples:
	- Abbreviations, function keys, hot keys, command keys, macros, aliases, templates, type-ahead, bookmarks, hot links, history, default values, etc.
\end{itemize}
\item Good error messages. 
\begin {itemize}
\item The messages should be informative enough such that users can understand the nature of errors, learn from errors, and recover from errors. 
\item Phrased in clear language, avoid obscure codes. Example of obscure code: “system crashed, error code 147.”
\item Precise, not vague or general. Example of general comment: “Cannot open document.”
\item Constructive.
\item Polite. Examples of impolite message: “illegal user action,” “job aborted,” “system was crashed,” “fatal error,” etc.
\end {itemize}
\item Prevent errors. It is always better to design interfaces that prevent errors from happening in the first place.
\begin {itemize} 
\item Interfaces that make errors impossible.
\item Avoid modes (e.g., vi, text wrap). Or use informative feedback, e.g., different sounds.
\item Execution error vs. evaluation error.
\item Various types of slips and mistakes.
\end {itemize}
\item Clear closure. Every task has a beginning and an end. Users should be clearly notified about the completion of a task. 
\begin {itemize}
\item Clear beginning, middle, and end.
\item Complete 7-stages of actions.
\item Clear feedback to indicate goals are achieved and current stacks of goals can be released. Examples of good closures include many dialogues.
\end {itemize}
\item Reversible actions. 
\begin {itemize}
\item Users should be allowed to recover from errors. Reversible actions also encourage exploratory learning. 
\item At different levels: a single action, a subtask, or a complete task.
\item Multiple steps.
\item Encourage exploratory learning.
\item Prevent serious errors.
\end {itemize}
\item Use users’ language. The language should be always presented in a form understandable by the intended users.
\begin{itemize}
\item Use standard meanings of words.
\item Specialized language for specialized group.
\item User defined aliases.
\item Users’ perspective. Example: “we have bought four tickets for you” (bad) vs. “you bought four tickets” (good).
\end {itemize}
\item Help and documentation. Always provide help when needed. 
\begin {itemize}
\item Context-sensitive help.
\item Four types of help.\\
-task-oriented;\\
-alphabetically ordered;\\
-semantically organized;\\
-search.
\item Help embedded in contents.
\end {itemize}
\item Users in control. Do not give users that impression that they are controlled by the systems. 
\begin {itemize}
\item Users are initiators of actors, not responders to actions.
\item Avoid surprising actions, unexpected outcomes, tedious sequences of actions, etc.
\end {itemize}
\end{enumerate}
\subsection{Tools}
\begin {enumerate} 
\item Downloaded OBS to record experiment sessions
\end {enumerate}
\subsection{To do}
\begin {enumerate}
 \item Detail plan
 \item Describe Pairwise methodology
 \item Define tasks
 \item prepare survey questions
 \end {enumerate}

\subsection{Task definition/selection criteria}
\begin {enumerate}
\item Tasks based on difficulty levels (Difficult, Medium and easy)
\item Commonly performed tasks (applicable to all the selected software)
\item Task that would/should generate errors messages or error codes
\item Tasks to check standards and conventions
\item Tasks that should provide users with the system's current state and what actions can be done or where to go or what change was made
\item Tasks related to what users will do in the real world
\item End to End tasks that require users to go through sequential or hierarchical steps.
\item Tasks that allow users to reuse a previously defined value without having to memorize or jot it.
\item Tasks that should provide users with feedback
\item Tasks that allow users to customize and use shortcuts, bookmarks, command keys etc.
\item Tasks to verify if the system is capable of preventing and /or reversing errors
\item Tasks that might lead the user to use help or documentation

\end {enumerate}

\subsection{Usability Questionnaire}
This questions need to be reworded to make them as open ended as possible\\
source \url{https://www.usabilitest.com/sus-pdf-generator}- 20-29
\begin {enumerate}
\item Overall, I am satisfied with how easy it is to use this system.
\item It was simple to use this system.
\item I could effectively complete the tasks and scenarios using this system.
\item I was able to complete the tasks and scenarios quickly using this system.
\item I was able to efficiently complete the tasks and scenarios using this system.
\item I felt comfortable using this system.
\item It was easy to learn to use this system.
\item I believe I could become productive quickly using this system.
\item The system gave error messages that clearly told me how to fix problems.
\item Whenever I made a mistake using the system, I could recover easily and quickly.
\item The information (such as online help, on-screen messages, and other documentation) provided with this system was clear.
\item It was easy to find the information I needed.
\item The information provided for the system was easy to understand.
\item The information was effective in helping me complete the tasks and scenarios.
\item The organization of information on the system screens was clear.
\item The interface of this system was pleasant.
\item I liked using the interface of this system.
\item This system has all the functions and capabilities I expect it to have.
\item Overall, I am satisfied with this system.
\item I think that I would like to use this system frequently.
\item I found the system unnecessarily complex.
\item I thought the system was easy to use.
\item I think that I would need the support of a technical person to be able to use this system.
\item I found the various functions in this system were well integrated.
\item I thought there was too much inconsistency in this system.
\item I would imagine that most people would learn to use this system very quickly.
\item I found the system very cumbersome to use.
\item I felt very confident using the system.
\item I needed to learn a lot of things before I could get going with this system.
\end {enumerate}
\section{Analytic Hierarchy Process}
